Time and space specifications for stencils

### 2016-05-20 paper.tex
revised DNF grammar; prior to removing it

@@

\begin{SpecVerbatim}[xleftmargin=0.1cm]
20-24  u: centered depth=1 dim=1
26-30  u: centered depth=1 dim=2
       v: forward depth=1 dim=1, backward depth=1 dim=1
32-33  u: centered depth=1 dim=1,2
\end{SpecVerbatim}
(b). Inferred stencil specification from CamFort
\caption{Fragment of Navier-Stokes fluid simulator and its specification}
\label{ref:navier-stokes-fragment}
\end{figure}

@@

Figure~\ref{fig:syntax}
gives the syntax, which we introduces in stages below. 
%%

\begin{figure}
\begin{align*}
\textit{specs} ::= & \; \textit{spec} \; \texttt{;} \; \textit{specs} \, \mid \, \textit{spec} \\
%
\textit{spec} :: = & \; \texttt{v} : S \\[0.5em]
S ::= &  \; \texttt{forward} \; [\texttt{depth=}\textit{depth}] \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{backward} \; [\texttt{depth=}\textit{depth}] \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{centered} \; [\texttt{depth=}\textit{depth}] \; \texttt{dims=}\textit{dims} \\
& \; \mid \texttt{unspecified} \; [\texttt{dims=}\textit{dims}] \\
& \; \mid \texttt{read-once} \; S \\[0.5em]
\textit{depth} ::= & \; \mathbb{N} \, \mid \, \textit{temp-spec} \\ 
\textit{temp-spec} ::= & \; \mathbb{N}\{var\} \\
\textit{dims} ::= & \; \mathbb{D} \; \texttt{,} \; \textit{dims} \, \mid
                    \, \mathbb{D} \\
\mathbb{D}  ::= & \; \mathbb{N}_{>0} \, \mid \, \texttt{t}
\end{align*}
\caption{Syntax of specifications}
\label{fig:syntax}
\end{figure}

@@

\begin{figure}
\begin{align*}
\hspace{-2em}
\begin{array}{c}
\hspace{-1em}
\setlength{\arraycolsep}{0.1em}
\begin{array}{rl}
\interp{\textit{spec}; \textit{specs}} & = \interp{spec} \cup
  \interp{\textit{specs}} \\
%% TEMPORAL SPECS
% \interp{\texttt{v} : \texttt{forward} \; \texttt{depth}=n\texttt{\{u\}} \;
%  \texttt{dims=t}} & =  \{ (\texttt{u}, \textit{ix})^m \mid \forall m,
%                     ix : \mathbb{Z}^{\mathbb{D}}, \textit{ix} \,
%                     \texttt{t} = 0 \} \\[0.4em]
%% SPATIAL SPECS
\interp{\texttt{v} : S} & = \{(\texttt{v}, ix)^m \mid ix^m \in
  \interp{S}\} \\
\end{array}\\[1em]
%\framebox{$\interp{S}$} \\[1em]
\begin{array}{ll}
& \interp{\texttt{reflexive}}
  = \\
& \hspace{0.9em}  \{ ix^m \mid \forall m, \, ix : \relix, d : \mathbb{D}
  \, . \, d \in \textit{ds} \Rightarrow ix \, d = 0 \} \\[0.4em]
& \interp{\texttt{forward} \;\; \texttt{depth}=n \;\;
  \texttt{dims}=\textit{ds}}  = \;\; (\texttt{t} \not\in ds) \\
& \hspace{0.9em}  \{ ix^m \mid \forall m, \, ix : \relix, d : \mathbb{D}
  \, . \, d \in \textit{ds} \Rightarrow 0 \leq (ix \, d) \leq n \} \\[0.4em]
& \interp{\texttt{backward} \;\; \texttt{depth}=n \;\; \texttt{dims}=\textit{ds}}
  = \; \; (\texttt{t} \not\in ds) \\
& \hspace{0.9em}  \{ ix^m \mid \forall m, \, ix : \relix, d : \mathbb{D}
  \, . \, d \in \textit{ds} \Rightarrow (-n) \leq (ix \, d) \leq 0 \}
  \\[0.4em]
& \interp{\texttt{read-once} \; S} = \{ ix^1 \mid ix^m \in \interp{S}
  \} 
\end{array}
\end{array}
\end{align*}
\textit{$a^m \in A$ means there are $n$ copies of $a$ in
  the multi-set $A$}
\caption{Multi-set model of specifications}
\label{fig:model}
\end{figure}

>>>>

% Syntax macros
\newcommand{\stenFwd}[2]{\texttt{forward} (\texttt{depth}=#1,
  \texttt{dim}=#2)}
\newcommand{\stenBwd}[2]{\texttt{backward} (\texttt{depth}=#1,
  \texttt{dim}=#2)}
\newcommand{\stenCen}[2]{\texttt{backward} (\texttt{depth}=#1,
  \texttt{dim}=#2)}

@@

%\begin{SpecVerbatim}[xleftmargin=0.1cm]
%20-24  u: centered depth=1 dim=1
%6-30  u: centered depth=1 dim=2
%      v: forward depth=1 dim=1, backward depth=1 dim=1
%32-33  u: centered depth=1 dim=1,2
%\end{SpecVerbatim}

\begin{SpecVerbatim}[xleftmargin=0.3cm]
%= stencil (centered, depth=1, dim=1)
%=       + (centered, depth=1, dim=2) :: u

%= stencil (forward, depth=1, dim=1)
%=       + (backward, depth=1, dim=1) :: v
\end{SpecVerbatim}
(b). Inferred stencil specification from CamFort
\caption{Fragment of Navier-Stokes fluid simulator and its specification}
\label{ref:navier-stokes-fragment}
\end{figure}

@@

Figure~\ref{fig:syntax}
gives the syntax, which we introduces in stages below.
The top-level is given by the \textit{spec} production
which splits into either a \textit{spatial} specification or
a \textit{temporal specification}.
%%

\begin{figure}[t]
\begin{align*}
\def\arraystretch{1.2}
\begin{array}{rl}
\textit{spec} ::= \; & \textit{spatial} \mid \textit{temporal}   \\ \\
\textit{spatial} ::= \; & [\textit{mod} \; \{, \textit{mod} \}] \; \textit{sumS} \\
\textit{mod} ::= \; &
 \texttt{read-once} \\
& \mid \texttt{reflexive} \; \texttt{dim=}\textit{dim}{\texttt{,}} \\
& \mid \texttt{irreflexive} \; \texttt{dim=}\textit{dim}{\texttt{,}} \\
\textit{sumS} ::= \; & \textit{prodS} \;\, \texttt{+} \;\, \textit{sumS} \mid S_{\texttt{+}} \; \texttt{+}
          \; \textit{sumS} \mid \epsilon \\
\textit{prodS} ::= \; & S_{\texttt{*}}  \;\, \texttt{*} \;\, prodS
                        \mid \epsilon \\ \\
\textit{temporal} ::= \; & \texttt{dependency} \; (v \; \{ , v \})  \\ \\
\multicolumn{2}{l}{(\textit{meta rules, where \textnormal{$\odot = \{\texttt{*}, \texttt{+}, \texttt{,}\}$}})} \\
S_\odot ::= \; & \texttt{forward} \; [,\texttt{depth=}\mathbb{N}] \;
        , \texttt{dims=}\textit{dims}_\odot  \\
\mid \; & \texttt{backward} \; [,\texttt{depth=}\mathbb{N}] \; , \texttt{dims=}\textit{dims}_\odot \\
\mid \; & \texttt{centered} \; [,\texttt{depth=}\mathbb{N}] \; ,
          \texttt{dims=}\textit{dims}_\odot \\
\textit{dims}_\odot ::= & \; \mathbb{N}_{>0} \; \odot \;
                          \textit{dims}_{\odot} \; \mid \;
                          \mathbb{N}_{> 0}
\end{array}
\end{align*}
\caption{Specification syntax}
\label{fig:syntax}
\end{figure}

@@

\begin{figure}
\input{model.tex}
%\textit{$a^m \in A$ means there are $n$ copies of $a$ in
%  the multi-set $A$}
\caption{Multi-set model of specifications}
\label{fig:model}
\end{figure}
